---
title: "Assignment 3"
author: "Jee Ong 47086998"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document: default
  pdf_document: default
bibliography: referencelist.bib
---

## Exercise 1

```{r load_data, echo=TRUE, message=FALSE, warning=FALSE}
library("tidyverse")
library("devtools")
library("glue")
library("dplyr")
library("stringr")
library("ggplot2")
library("knitr")
library("ggrepel")
passwords <- read_csv("passwords.csv")

# Get the Data (Provided on github)

# passwords <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-01-14/passwords.csv')

# Or read in with tidytuesdayR package (https://github.com/thebioengineer/tidytuesdayR)
# PLEASE NOTE TO USE 2020 DATA YOU NEED TO UPDATE tidytuesdayR from GitHub

# Either ISO-8601 date or year/week works!

# Install via 
#devtools::install_github("thebioengineer/tidytuesdayR", force = TRUE)

#tuesdata <- tidytuesdayR::tt_load('2020-01-14') 
tuesdata <- tidytuesdayR::tt_load(2020, week = 3)

#passwords <- tuesdata$passwords

```

### INIT

```{r plot1, echo=TRUE}



```



## Exercise 2

**Not required**, but you're welcome to put a link to your R package on GitHub here for completeness if your GitHub account is not private. For example, click [here](https://github.com/hadley/emo) to see the emoji package.


## Exercise 3

### Chi-squared Tests for independence

This [link](https://rpruim.github.io/s341/S19/from-class/MathinRmd.html) is helpful to formatting maths in RMarkdown. You will see it includes Greek letters, including $\chi^2$. 

Some questions you might like to consider here

- what is the null and alternative hypothesis? $H_0=\text{hmmm what's this?}$ and $H_1=\text{hmmm..}$
- what is the formula for the chi-squared test statistic?
- how do you calculate the expected values?
- to help explain the chi-squared test, work through the example provided in the assignment question and show your working. You can check your $\chi^2$ statistic in R using a package for chi-squared tests and get the p-value for your analysis. Do you reject or fail to reject the null hypothesis?
- some packages in R that can do chi-squared tests:
    - `stats` 
    - `janitor` 
    - to get the citation for these packages, in the R console run `citation("stats")` or `citation("janitor")`
    
Here is an example of how to include references in your assignment in RMarkdown - the `referencelist.bib` file can be downloaded from iLearn under week 9 material and this file has been included on line 8 of `A2_template.Rmd`. Here is a book by @boas2006mathematical and an article by @lustri2018nanoptera and the `mpcmp` package @mpcmp. These have nothing to do with chi-squared tests so don't reference these in your assignment.

### Fisher’s Exact test

### Testing if Fisher’s Exact test is conservative

## References
