---
title: "STAT 1378"
subtitle: "Assignment 3: Investigation of top 500 passwords. "
date: "`r format(Sys.time(), '%d %B %Y')`"
fontsize: 10pt
classoption: "aspectratio=169"
output: 
  beamermq::macquarie:
     keep_tex: yes
     toc: no
     incremental: true
     texmflocal: no
bibliography: references.bib
---

```{r setup, include=FALSE}
library("tidyverse")
library("devtools")
library("glue")
library("dplyr")
library("stringr")
library("ggplot2")
library("knitr")
library("ggrepel")
passwords <- read_csv("passwords.csv")

# Get the Data (Provided on github)

# passwords <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-01-14/passwords.csv')

# Or read in with tidytuesdayR package (https://github.com/thebioengineer/tidytuesdayR)
# PLEASE NOTE TO USE 2020 DATA YOU NEED TO UPDATE tidytuesdayR from GitHub

# Either ISO-8601 date or year/week works!

# Install via 
#devtools::install_github("thebioengineer/tidytuesdayR", force = TRUE)

#tuesdata <- tidytuesdayR::tt_load('2020-01-14') 
#tuesdata <- tidytuesdayR::tt_load(2020, week = 3)

#passwords <- tuesdata$passwords
passwordsFiltered <- passwords[!is.na(passwords[,1]),]

```

## Main Investigation

>- Investigation of top 500 passwords. 
>- 2 main questions:
>- Which Category has the weakest passwords?
>- Does having a stronger password affect how long it takes to crack it?
>- Finals Conclusions. 
>- Other Recommendations. 
>- References

## My Data:

Variables:

>1. \alert{Rank} (Which is the most COMMON password)
>2. \alert{Password} (The password itself).
>3. \alert{Value} (Time to crack by online guessing)
>4. \alert{TimeUnit} (The metric of time for a password brute force.)
>5. \alert{OfflineCrackSec} (The amount of seconds for a password to be cracked)
>6. \alert{Strength} (Strength of password according to security.org)
>7. \alert{Font size}

## Hypothesis:
>1. Most exploitable category are names.
>2. Name will have the shortest time to be cracked.
>3. There IS a relationship between rank and strength
>4. There is a correlation between strength and value 

# Datasets 

## Most Exploitable Category. 

```{r, echo = FALSE, fig.align='center', out.width="80%"}
name <- names(passwordsFiltered)
plot4Data <- filter(passwordsFiltered)
  ggplot(plot4Data) +
  geom_col(aes(x = rank, y = category)) +
  ggtitle(glue::glue("Bar Chart of Most Exploitable category"))
```

## Cateogry of the strongest and weakest passwords. 

```{r plot2, echo=FALSE, fig.align='center', out.width="80%"}
p2 <- ggplot(data = passwordsFiltered) +
  geom_bar(aes(x = strength, y = category),
  stat = "identity", position = "dodge") +
ggtitle(glue::glue("Plot 2: A {name[8]} vs {name[3]} Stacked Histogram"))

p2
```
## Category of the strength vs time to crack in s

```{r plot2a, echo=FALSE, fig.align='center', out.width="80%", warning=FALSE, message=FALSE}
passwords$logtime <- log(passwords$offline_crack_sec)
passwords %>%
  filter(category == "name") %>%
  ggplot(aes(x = logtime, y = strength)) +
  geom_point() +
  geom_smooth() +
  ggtitle(glue::glue("Plot 3: A logtime vs {name[8]} Test"))


```


## Rank vs Strength ScatterPlot

```{r plot3d, echo=FALSE, fig.align='center', message = FALSE, out.width="80%"}
plot4 <- passwordsFiltered %>%
    filter(category == "name") %>%
    ggplot(aes(x = rank, y = strength)) +
    geom_point() +
    geom_smooth() +
    ggtitle(glue::glue("Plot 4: A {name[1]} vs {name[8]} Test"))

plot4
```

# Correlation Test

```{r correlation, echo = TRUE}

correlation <- cor(x = passwordsFiltered$rank, y = passwordsFiltered$strength)

correlation
```


## Value vs Strength Scatter plot. 

```{r scatterAttempt, echo=FALSE, fig.align='center', out.width="80%", message = FALSE}
  plot5Draft <- passwordsFiltered %>% 
  filter(rank < 500)
  plot5 <- ggplot(plot5Draft, aes(x = value, y = strength)) + 
  geom_point() + 
  geom_smooth() +
  ggtitle(glue::glue("Scatterplot of {name[4]} vs {name[8]}")) + 
  xlab(name[4]) + 
  ylab(name[8])
  
  plot5
```

# Conclusions

>- Name was the most common password category. 
>- The time to crack some passwords took longer, regardless of what category. 
>- There IS NO linear regression between rank and strength. 
>- There IS a linear regression between strength and Time to crack. 
>- There is NO linear regression between value and strength. 

# Other Reccomendations:

## Password Manager: 

>- Minimises chances of password being guessed with RNG password generation. 
>- Bitwarden changes the strength of the password.
>- Through our observation, this will make more unique passwords that would not be categorized. As we realise, that passwords categorised as a name I.e. Fluttershy is more common than a RNG one. 

## References

@grilo2021towards
@suo2005graphical
@tidyTuesday
