---
title: "STAT 1378: A Thomas Fung Appreciation Society"
subtitle: "Assignment 3"
date: "`r format(Sys.time(), '%d %B %Y')`"
fontsize: 10pt
classoption: "aspectratio=169"
output: 
  beamermq::macquarie:
     keep_tex: yes
     toc: no
     incremental: true
     # Change texmflocal to yes if you install the template files into your local tex installation.
     texmflocal: no
bibliography: references.bib
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE, cache=TRUE)
library("tidyverse")
library("devtools")
library("glue")
library("dplyr")
library("stringr")
library("ggplot2")
library("knitr")
library("ggrepel")
passwords <- read_csv("passwords.csv")

# Get the Data (Provided on github)

# passwords <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-01-14/passwords.csv')

# Or read in with tidytuesdayR package (https://github.com/thebioengineer/tidytuesdayR)
# PLEASE NOTE TO USE 2020 DATA YOU NEED TO UPDATE tidytuesdayR from GitHub

# Either ISO-8601 date or year/week works!

# Install via 
#devtools::install_github("thebioengineer/tidytuesdayR", force = TRUE)

#tuesdata <- tidytuesdayR::tt_load('2020-01-14') 
tuesdata <- tidytuesdayR::tt_load(2020, week = 3)

#passwords <- tuesdata$passwords

```



# Intro

## Slide with bullets

- Bullet 1
- Bullet 2
- Bullet 3

Use `\alert` to \alert{highlight} some text

### Some enumeration

1. The first item
1. Stuff
1. Nonsense

# Using R

## Slide with R output

```{r p1, echo = TRUE}
  plot1 <- passwords %>%
  filter(category == "animal")
  ggplot(data = plot1) +
  geom_line(mapping = aes(x = strength, y = offline_crack_sec)) +
  facet_wrap(~plot1$password, scales = "free") +
  labs(title = "Plot #1: How the Three Lap (with no shortcut) develops overtime")
  
  plot1
```

```{r p1, echo = TRUE}
  plot1 <- passwords %>%
  filter(rank < 500)
  ggplot(data = plot1) +
  geom_line(mapping = aes(x = strength, y = offline_crack_sec)) +
  facet_wrap(~plot1$category, scales = "free") +
  labs(title = "Plot #1: The category with the most exploitable passwords")
  
  plot1
```


## Slide with graphics

```{r plot2, echo=TRUE, message=TRUE, fig.align='center'}
plot2 <- passwords %>%
    filter(time_unit == "years" && rank < 100) %>%
    group_by(interaction(strength,offline_crack_sec)) %>%
    # mutate(Banana = paste(type,ifelse(shortcut == "Yes", "With Shourtcut","Without Shortcut"))) %>%
    # ggplot(aes(x = date, y = time, color = Race)) +
    ggplot(aes(x = strength, y = offline_crack_sec)) +
    geom_point() +
    geom_line() +
    labs(title = "Plot 2: A strength vs time crack chart", subtitle = "?", x = "Strength", y = "crack time")

plot2

# i want a histogram here
# i want advice on what i should look for in the histogram
```

```{r plot2, echo=TRUE, message=TRUE, fig.align='center'}
plot2 <- passwords %>%
    filter(rank < 100) %>%
    group_by(interaction(strength,offline_crack_sec)) %>%
    # mutate(Banana = paste(type,ifelse(shortcut == "Yes", "With Shourtcut","Without Shortcut"))) %>%
    # ggplot(aes(x = date, y = time, color = Race)) +
    ggplot(aes(x = strength, y = offline_crack_sec)) +
    geom_point() +
    geom_line() +
    labs(title = "Plot 2: A strength vs time crack chart", subtitle = "?", x = "Strength", y = "crack time")

plot2

# i want a histogram here
# i want advice on what i should look for in the histogram
```

```{r}
  name <- names(passwords)
  # Filter me?
  fit0 <- lm(offline_crack_sec ~ value, data = passwords)
  plot3 <- ggplot(passwords, aes(x = rank, y = strength)) + 
  geom_point() + 
  ggtitle(glue::glue("Scatterplot of {name[1]} vs {name[8]}")) + 
  xlab(name[1]) + ylab(name[2])
  
  plot3
```



## Slide with mathematics

Suppose $X_1, X_2, \ldots, X_n$ are independent and identitically distributed random variables with common cumulative distribution function $F_X$ with support on $\mathbb{R}$. The empirical cumulative distribution function is defined with,
\[
  F_n(x) = \frac{1}{n}\sum_{i = 1}^n I_{\left( -\infty, x\right]}(X_i)
\]
where $I_A(x)$ denotes the indicator function for the set $A$. The following theorem provides uniform covergence for $F_n$


:::{.block}
### Glivenko-Cantelli Theorem
If $X_i$ are i.i.d. with common cdf $F$ then,
\[
  \left\| F_n - F \right\| = \sup_{x \in \mathbb{R}} |F_n(x) - F(x)| \stackrel{n \to \infty}{\longrightarrow} 0\quad \text{almost surely.}
\]
:::

* See @vanderVaart.Wellner:96 for more information on Empirical processes.

---

A slide with no header if you need more space.

# RMarkdown Examples

## R Figure

```{r mtcarsboxplot, echo = TRUE}
plot(mpg ~ cyl, data = mtcars)
```

## R Table

A simple `knitr::kable` example:

\small

```{r kableEx, echo=TRUE}
knitr::kable(head(mtcars),
       caption="First few observations of the mtcars dataset")
```

## Resources

* See the [RMarkdown repository](https://github.com/rstudio/rmarkdown) for more on RMarkdown
* Also the 

## References
